Figures

### 2019-06-23 figures/09_stream_buffer.Rmd
suppress pkg msgs
explore different buffer contrasts

```{r 09_stream_buffer, echo=FALSE, fig.height=3, fig.width=4}
dt <- readRDS("../data/dt.rds") %>%
  dplyr::filter(stream_ag > 0) %>%
  mutate(diff = stream_ag - ag, 
         category = cut(diff, breaks = c(Inf, 25, -25, -Inf))) %>%
  drop_na(diff) %>%
  dplyr::select(lagoslakeid, ag, stream_ag, 
                diff, category, iws_ha) %>%
  arrange(diff)

# first llid is a low stream ag lake
# second llids is a high stream ag lake
llids <- c("4532", "96236")

@@

library(curl)
library(glue)
library(slippymath)
library(rgdal)

>>>>

```{r 09_stream_buffer, echo=FALSE, fig.height=3, fig.width=4, warning=FALSE}
dt <- readRDS("../data/dt.rds") %>%
  dplyr::filter(stream_ag > 0) %>%
  mutate(diff = stream_ag - ag, 
         category = cut(diff, breaks = c(Inf, 25, -25, -Inf))) %>%
  drop_na(diff) %>%
  dplyr::select(lagoslakeid, ag, stream_ag, 
                diff, category, iws_ha) %>%
  arrange(diff)

# first llid is a low stream ag lake
# second llid is a high stream ag lake

llids <- c("6992", "7026")

@@

library(curl)
suppressMessages(library(glue))
library(slippymath)
suppressMessages(library(rgdal))
